\subsection{Initial Formulation}
This initial formulation is due to Rebecca's thesis work.  We augment the species in the 
reduced model by $\na$ ``catchall'' species which are intended to mimic the effect of the 
species that were neglected in going from the detailed to the reduced model.  Catchall 
species and their quantities are denoted with a supersript $\prime$.  The species 
concentrations are now given by 
$\x = \left[x_{1}, \ldots, \x_{\nsr}, \x_{\nsr+1}, \ldots, \x_{\nsr + \na}\right]^{\dagger}$ 
where $\na$ is the number of atoms in the system.  The enthalpies are augmented similarly.  
We therefore introduce an enhanced reduced model of the form,
\begin{align}
  \odeone{\x}{t} &= \rr + \left[\Sop \x + \rrc\right] \label{eq:inad_reb} \\
  \odeone{T}{t}  &= \frac{-\displaystyle \h\lr{T}\cdot\odeone{\x}{t} + \dot{\mathcal{Q}}}
                         {\displaystyle \cp\lr{T}\cdot\x}. \label{eq:energy_reb}
\end{align}
The operators $\Sop$ and $\rrc$ are stochastic in nature and have several parameters that 
must be calibrated.  We must also specify a form for the enthalpies of the ``catchall'' 
species.  This was done by assuming a simple linear temperature dependence of the specific 
heat on the temperature.  In general,  
\begin{align}
  \hic{k} = \sum_{i=0}^{p}{\alpha_{ki}T^{i}}
\end{align}
and 
\begin{align}
  \cpic{k} = \sum_{i=1}^{p}{i\alpha_{ki}T^{i-1}}
\end{align}
where $p-1$ is the polynomial order being used to represent the specific heat.  Note that 
using~\eqref{eq:s_cp_rel} we have the additional relationship 
\begin{align}
  \sic{k} = \gamma_{k0} + \alpha_{k1}\ln\lr{T} + \sum_{i=2}^{p}{\frac{i}{i-1}\alpha_{ki}T^{i-1}}.
\end{align}
When $p=2$ we have simply 
\begin{align}
  \hic{k}  &= \alpha_{k0} + \alpha_{k1}T + \alpha_{k2}T^{2} \\ 
  \cpic{k} &= \alpha_{k1} + 2\alpha_{k2}T \\
  \sic{k}  &= \gamma_{k0}  + \alpha_{k1}\ln\lr{T} + 2\alpha_{k2}T.
\end{align}

